
{\bf structure of proposal}

\begin{enumerate}

 \item intro section on problem statement: a problem of access, and
   shortcomings of existing systems. Main point: EDURange can be as
   good as other systems in terms of curriculur material, but has less
   of the shortcomings of other environments. So the key purpose of
   this grant is to provide continued access to EDURange {as an
     alternative} free-of-charge to instructors {and} ease their
   access by providing a ``help desk'' of students who are actively
   involved in the development and management of EDUrange. We need the
   grant because faculty absolutely want shrink-wrapped access to
   non-trivial interesting exercises. State learning goals. State outcomes/objectives.

   Close the first section with a high-level overview of the proposal
   structure. Add value, stakeholders, resources, milestones.

   Use workshop feedback: our stakeholders need exactly this tool.

 \item 
 
   First discuss EDURange infrastructure

   a section on current Modules and their structure; this
   foreshadows the Assessment Plan. Modules include: Recon,
   ELFInfection, strace, scapyhunt, calculator grammar fuzzing,

   Description of exericse. analysis skills nurtured, cs 2013 curriculum topic.
   
   List of analysis skills.

   Modules are also an opportunistic mechanism: they provide a
   jumping-off point for discussing a variety of topics mapped to
   a -- exercise motivates each topic discussion or lesson.


 \item the webinar; the course template outline...make the point that
   the course is an example educational environment where EDURange can
   be mapped to or used.

 \item a section on the EDURange ``help desk'' (another core expense
   item)

 \item ongoing support for EDURange

 \item section on Assessment Plan -- this section will have 2
   sub-parts. One on raw metrics of number of users, etc. The second
   is on how well the EDURange infrastructure and scenarios map to the
   skills and knowledge of security throughout the CS 2013 undergrad
   curriculum. Assessment plan describes the assessment mechanisms,
   procedures, and practices

 \item Management Plan and milestones

 \item Data management plan (1 page)

\end{enumerate}
